State of the Practice for Lattice Boltzmann Method Software

### 2021-12-14 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
update RQs to be specific to LBM

\begin{enumerate}
	\item What artifacts are present in current software packages? 
	\item What tools (development, dependencies, project management) are used by
	current software packages?
	\item What principles, processes, and methodologies are used in the development
	of current software packages?
	\item What are the pain points for developers working on research software
	projects?  What aspects of the existing processes, methodologies and tools do
	they consider as potentially needing improvement?  How should processes,
	methodologies and tools be changed to improve software development and
	software quality?
	\item For research software developers, what specific actions are taken to
	address the following:
	\begin{enumerate}
		\item installability
		\item correctness and verifiability
		\item reliability
		\item robustness
		\item performance
		\item usability
		\item maintainability
		\item modifiability
		\item reusability
		\item understandability
		\item traceability
		\item visibility and transparency
		\item reproducibility
		\item unambiguity
	\end{enumerate} 
	\item How does software designated as high quality by this methodology
	compare	with top rated software by the community?
\end{enumerate}

@@

Table~\ref{} presents a summary of the software that was measured.  The table
shows the differences between the packages based on features.  \wss{Add some
discussion of some example features.}  The sections below summarize how the
software packages compare based on qualities, as measured by the measurement
template.   The results of the AHP ranking are also discussed.

>>>>

\begin{enumerate}
	\item What artifacts are present in current LBM packages? 
	\item What tools (development, dependencies, project management) are used by
	current LBM solvers?
	\item What principles, processes, and methodologies are used in the development
	of current LBM packages?
	\item What are the pain points for developers working on LBM software
	projects?  What aspects of the existing processes, methodologies and tools do
	they consider as potentially needing improvement?  How should processes,
	methodologies and tools be changed to improve software development and
	software quality?
	\item For LBM software developers, what specific actions are taken to
	address the following:
	\begin{enumerate}
		\item installability
		\item correctness and verifiability
		\item reliability
		\item robustness
		\item performance
		\item usability
		\item maintainability
		\item modifiability
		\item reusability
		\item understandability
		\item traceability
		\item visibility and transparency
		\item reproducibility
		\item unambiguity
	\end{enumerate} 
	\item How does software designated as high quality by this methodology
	compare	with top rated software by the community?
\end{enumerate}

@@

Before discussing quality differences between the packages and the results of
the AHP ranking, we will contrast the different packages based on features, as
shown in Table~\ref{tbl_features}. \wss{Add some discussion of some example
features.  Add Non-Newtonian and Fluid Structure interaction.  Listed in
alphabetical order.}  The sections below summarize how the software packages
compare based on qualities, as measured by the measurement template.   The
results of the AHP ranking are also discussed.
